Tables with \textbf{xtable} and \textbf{knitr}

### 2016-10-11 src/ArticleReadyTableGenerate.Rnw
table is  now visible. is formatted properly. needs to be repeated for all sides and regions

<<echo=FALSE, results='asis' >>=

  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)

  for (side in sides){
    for ( i in 1:7 ) {
      for (j in 1:3){
        test.type <-  hypothesis_ordinality[j]
        for (k in 0:2){
          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value

@@

    }
  }
  colnames(p_value_table)<- col_names
  p_value_table_print <- mapply(p_value_table, function(x){if (x<1E-4) return ("<0.0001") else{
    return(as.character(x,digits=4))
  }})
  xtab.out <- xtable(p_value_table_print)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#

>>>>

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline

<<echo=FALSE, results='asis' >>=
 convert_to_paper_style <- function(x) {
   if (x<1E-4) {
   return ("<0.0001") 
   } else {
    return (format(x,digits=4))
   }
 }
  simp.colnames<- function(x) {
     y = lapply(x,strsplit,"_",fixed=TRUE)
     #return(y)
     z = sapply(y , function(l) l[[1]][[1]])
     #z = gsub(".", " ",y)
    return (z)
  }
  make_matrix_printable <- Vectorize(convert_to_paper_style)
  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep="_")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)
  p_val_table_list<-list()
  xtablelist<- list()
  for (side in sides){
    for ( i in 1:7 ) {
      for (j in 1:3){
        test.type <-  hypothesis_ordinality[j]
        for (k in 0:2){
          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value

@@

    }
    colnames(p_value_table)<- col_names
  table_dims<- dim(p_value_table)
  p_value_table_print <- make_matrix_printable(p_value_table )
  dim(p_value_table_print) <- table_dims
  colnames(p_value_table_print) <- col_names
  rownames(p_value_table_print) <- comparison_strings
  #print(str(p_value_table_print))

  xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
  p_val_table_list[[side]]<- p_value_table_print
  xtablelist[[side]]<-xtab.out

  }
   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",names(p_val_table_list))
   xtablelist <- xtableList(p_val_table_list)
  addtorow <- list()
  addtorow$pos <- list(-1)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtableList (xtablelist, add.to.row = addtorow, only.contents=FALSE,
    include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
    type="latex")
# create a table of 7 comparisons
